For Finitary Induction-Induction, \\ Induction is Enough

### 2020-05-03 paper/paper.tex
stuff

The notion of morphism is determined by the notion of algebra
\cite{large_inf_qiit}, but we include it here for completeness.
\begin{definition}[Signature morphism, $\SignMor$]\label{def:morphism}
  A morphism from signature algebras $M$ to $N$ denoted
  $\SignMor\,M\,N$ consists of four functions and 17 equalities
  expressing that the functions preserve the operations of the two
  algebras. We use the same naming as in \Cref{def:algebra} and use
  superscripts to denote which algebra is meant.
\begin{alignat*}{5}
  & \rlap{(1) Substitution calculus} \\
  & \Con && : \Con^M && \ra\Con^N \\
  & \Ty  && : \Ty^M\,\GG && \ra\Ty^N\,(\Con\,\GG) \\
  & \Sub  && : \Sub^M\,\GG\,\GD && \ra\Sub^N(\Con\,\GG)\,(\Con\,\GD) \\
  & \Tm  && : \Tm^M\,\GG\,A && \ra\Tm^N\,(\Con\,\GG)\,(\Ty\,A) \\
  & \id && : \Sub\,\id^M && = \id^N \\
  & {\circ} && : \sigma\circ^M\delta && = \Sub\,\sigma\circ^N\Sub\,\delta \\
  & [] && : A[\sigma]^M && = \Ty\,A[\Sub\,\sigma]^N \\
  & [] && : t[\sigma]^M && = \Tm\,t[\Sub\,\sigma]^N \\
  & \boldsymbol{\cdot} && : \Con\,\boldsymbol{\cdot}^M && = \boldsymbol{\cdot}^N \\
  & \epsilon && : \Sub\,\epsilon^M && = \epsilon^N \\
  & \ext && : \Con\,(\GG\ext^M A) && = \Con\,\GG\ext^N\Ty\,A \\
  & , && : \Sub\,(\sigma,^M t) && = \Sub\,\sigma ,^N\Tm\,t \\
  & \pi_1 && : \Sub\,(\pi_1^M\,\sigma) && = \pi_1^N\,(\Sub\,\sigma) \\
  & \pi_2 && : \Tm\,(\pi_2^M\,\sigma) && = \pi_2^N\,(\Sub\,\sigma) \\
  & \rlap{(2) Universe} \\
  & \U && : \Ty\,\U^M && = \U^N \\
  & \El && : \Ty\,(\El^M\,a) && = \El^N\,(\Tm\,a) \\
  & \rlap{(3) Inductive parameters} \\
  & \Pi && : \Ty\,(\Pi^M\,a\,B) && = \Pi^N\,(\Tm\,a)\,(\Ty\,B) \\
  & \oldapp && : \Tm\,(t\mathbin{{\oldapp}^M} u) && = \Tm\,t\mathbin{{\oldapp}^N}\,\Tm\,u \\
  & \rlap{(4) External parameters} \\
  & \Pim && : \Ty\,(\Pim^M\,T\,B) && = \Pim^N\,T\,(\lambda\alpha.\Ty\,(B\,\alpha)) \\
  & \appm && : \Tm\,(t\mathbin{{\appm}^M}\alpha) && = \Tm\,t\mathbin{{\appm}^N}\alpha
\end{alignat*}
Given an $f:\SignMor\,M\,N$, we denote its first four components just
by $f_\Con$, $f_\Ty$, $f_\Sub$, $f_\Tm$ or just write $f$ if it is
clear which one is meant.
\end{definition}

@@

In this section we show that any model of ETT which supports indexed
W-types also supports the theory of signatures, and as a consequence
of \Cref{th:tosToIITs}, all IITs. For this, we work in the internal
language of a model of ETT supporting indexed W-types
\cite{indexedcont}. Indexed W-types correspond to the usual notion of
(possibly mutual) indexed inductive types. We will use Agda-style
notation for defining such inductive families: we list the sorts and
constructors and use pattern matching when eliminating from them. qFor
an encoding of mutual inductive families as families as indexed
W-types, see e.g.\ \cite{mutual}.

>>>>

The notion of morphism is determined by the notion of algebra
\cite{large_inf_qiit}, but we include it here for completeness.
\begin{definition}[Signature morphism, $\SignMor$]\label{def:morphism}
  A morphism from signature algebras $M$ to $N$ denoted
  $\SignMor\,M\,N$ consists of four functions and 17 equalities
  expressing that the functions preserve the operations of the two
  algebras. We use the same naming as in \Cref{def:algebra} and use
  superscripts to denote which algebra is meant.
\begin{alignat*}{5}
  & \rlap{(1) Substitution calculus} \\
  & \Con && : \Con^M && \ra\Con^N \\
  & \Ty  && : \Ty^M\,\GG && \ra\Ty^N\,(\Con\,\GG) \\
  & \Sub  && : \Sub^M\,\GG\,\GD && \ra\Sub^N(\Con\,\GG)\,(\Con\,\GD) \\
  & \Tm  && : \Tm^M\,\GG\,A && \ra\Tm^N\,(\Con\,\GG)\,(\Ty\,A) \\
  & \id && : \Sub\,\id^M && = \id^N \\
  & {\circ} && : \sigma\circ^M\delta && = \Sub\,\sigma\circ^N\Sub\,\delta \\
  & [] && : A[\sigma]^M && = \Ty\,A[\Sub\,\sigma]^N \\
  & [] && : t[\sigma]^M && = \Tm\,t[\Sub\,\sigma]^N \\
  & \boldsymbol{\cdot} && : \Con\,\boldsymbol{\cdot}^M && = \boldsymbol{\cdot}^N \\
  & \epsilon && : \Sub\,\epsilon^M && = \epsilon^N \\
  & \ext && : \Con\,(\GG\ext^M A) && = \Con\,\GG\ext^N\Ty\,A \\
  & , && : \Sub\,(\sigma,^M t) && = \Sub\,\sigma ,^N\Tm\,t \\
  & \pi_1 && : \Sub\,({\pi_1}^M\,\sigma) && = {\pi_1}^N\,(\Sub\,\sigma) \\
  & \pi_2 && : \Tm\,({\pi_2}^M\,\sigma) && = {\pi_2}^N\,(\Sub\,\sigma) \\
  & \rlap{(2) Universe} \\
  & \U && : \Ty\,\U^M && = \U^N \\
  & \El && : \Ty\,(\El^M\,a) && = \El^N\,(\Tm\,a) \\
  & \rlap{(3) Inductive parameters} \\
  & \Pi && : \Ty\,(\Pi^M\,a\,B) && = \Pi^N\,(\Tm\,a)\,(\Ty\,B) \\
  & \oldapp && : \Tm\,(t\mathbin{{\oldapp}^M} u) && = \Tm\,t\mathbin{{\oldapp}^N}\,\Tm\,u \\
  & \rlap{(4) External parameters} \\
  & \Pim && : \Ty\,(\Pim^M\,T\,B) && = \Pim^N\,T\,(\lambda\alpha.\Ty\,(B\,\alpha)) \\
  & \appm && : \Tm\,(t\mathbin{{\appm}^M}\alpha) && = \Tm\,t\mathbin{{\appm}^N}\alpha
\end{alignat*}
Given an $f:\SignMor\,M\,N$, we denote its first four components just
by $f_\Con$, $f_\Ty$, $f_\Sub$, $f_\Tm$ or just write $f$ if it is
clear which one is meant.
\end{definition}

@@

In this section we show that any model of ETT which supports indexed
W-types also supports the theory of signatures, and as a consequence
of \Cref{th:tosToIITs}, all IITs. For this, we work in the internal
language of a model of ETT supporting indexed W-types
\cite{indexedcont}. Indexed W-types correspond to the usual notion of
(possibly mutual) indexed inductive types. We will use Agda-style
notation for defining such inductive families: we list the sorts and
constructors and use pattern matching when eliminating from them. For
an encoding of mutual inductive families as families as indexed
W-types, see e.g.\ \cite{mutual}.
